Automatic Summarization of Scientific Texts

### 2018-06-09 paper/paper.tex
Added a sentence about our metric to the abstract
Removed old paragraphs from the paper

@@

\keywords{text summarization, NLP, GAN, reinforcement learning}

@@

\section{Problem statement}

The main hypothesis is that generative adversarial networks with reinforcement learning based generator, when applied to the problem of abstractive scientific text summarization, can provide better results than recent state-of-the-art approaches.

The model is provided with a labeled dataset.

@@

@@

\paragraph{Collecting paper IDs} We started by making requests to arXiv and parsing the response to acquire unique identifiers of each paper. These are the fixed-length strings that look like this: \textbf{1801.01587}. They allow us to access everything related to this paper (including its metadata and full text as PDF). We have only collected 2000 IDs from stat.ML category. We didn't collect all the papers because of network restrictions of arXiv API, huge amount of space required to store them, and the time required to process them. We might create a larger database of papers till the second evaluations, but for now a sample of 2000 random papers from one category will be enough.

@@

>>>>

We propose our own metric based on word-embeddings, which we believe will be more suitable for evaluation of abstractive summaries.

@@

\keywords{text summarization, NLP}

@@

@@

\paragraph{Collecting paper IDs} We started by making requests to arXiv and parsing the response to acquire unique identifiers of each paper. These are the fixed-length strings that look like this: \textbf{1801.01587}. They allow us to access everything related to this paper (including its metadata and full text as PDF). We have only collected 2000 IDs from stat.ML category. We didn't collect all the papers because of network restrictions of arXiv API, huge amount of space required to store them, and the time required to process them. Same approach can be used to collect more data, but for our problem a set of 2000 papers from one category is enough. For example, DUC (Document Understanding Conference) dataset which is among the most commonly used in the feld of text summarization has 30 sets with approximately 10 documents each\footnote{\url{https://www-nlpir.nist.gov/projects/duc/guidelines/2001.html}}.

\subsection{Examples}

@@

@@

Evaluating a summary is a difficult task because there does not exist an ideal summary for a given document or set of documents. \cite{das-7}. Manual evaluation is too expensive, so we will only be considering the automatic techniques.

Automatic evaluation metrics compare manually written ideal summaries with summaries generated automatically by summarization systems.
